DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-26 paper/overview.tex
Update platform overview

In this section, we provide an overview of our DeepPicar platform. In
developing DeepPicar, one of our primary goals is to replicate the
NVIDIA's DAVE-2 system on a smaller scale with using a low cost
multicore platform, Raspberry Pi 3. Because the Pi 3's computing
performance is much lower than that of the DRIVE PX platform used in
DAVE-2, we are interested in if, and how, we can process
computationally expensive neural network operations in
real-time. Specifically, inferencing (forward pass processing)
operations must be completed within each control period
duration---e.g., a WCET of 50ms for 20Hz control frequency---locally on
the Pi 3 platform, although training of the network (back-propagation
for weight updates) can be done offline and remotely using a desktop
computer.

@@

For the neural network architecture, we adopt a TensorFlow version of
NVIDIA DAVE-2's convolutional neural network (CNN), published by Dr.
Fridman at  MIT~\footnote{https://github.com/lexfridman/deeptesla}. As
in DAVE-2, the CNN takes a raw color image (200x66 RGB pixels)
as input and produces a single steering angle value as
output. Figure~\ref{fig:architecture} shows the network architecture, which
is comprised of 9 layers, 250K parameters, and about 27 million
connections.

\begin{figure}[t]
  \centering
  \includegraphics[width=.6\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

Another issue we observed in training/testing the network, which could
affect the network performance, is camera latency. In DeepPicar's
context, the camera latency is from the time the camera
sensor observes the scene to the time the computer actually reads the
digitized image data. This time can be noticable depending on the camera 
used and the performance of the Pi. We experimentally measure the camera
latency and found it to be around 50-100 ms. This is higher than the 
latency of human perception, which is known to be as fast as 13 
ms~\cite{ThomasBurger2015}. Higher camera latency could negatively 
affect control performance, because the DNN would analyze stale scenes. 
In the future, we plan to identify and use low-latency cameras.

>>>>

In this section, we provide an overview of our DeepPicar platform. In
developing DeepPicar, one of our primary goals is to replicate the
NVIDIA's DAVE-2 system on a smaller scale with using a low cost
multicore platform, the Raspberry Pi 3. Because the Pi 3's computing
performance is much lower than that of the DRIVE PX platform used in
DAVE-2, we are interested in if, and how, we can process
computationally expensive neural network operations in
real-time. Specifically, inferencing (forward pass processing)
operations must be completed within each control period
duration---e.g., a WCET of 33.$\overline{\mbox{33}}$ ms for 30Hz control 
frequency---locally on the Pi 3 platform, although training of the 
network (back-propagation for weight updates) can be done offline and 
remotely using a desktop computer.

@@

For the neural network architecture, we adopt a TensorFlow version of
NVIDIA DAVE-2's convolutional neural network (CNN), published by Dr.
Fridman at  MIT~\footnote{https://github.com/lexfridman/deeptesla}. As
in DAVE-2, the CNN takes a raw color image (200x66 RGB pixels)
as input and produces a single steering angle value as
output. Figure~\ref{fig:architecture} shows the network architecture, which
is comprised of 8 layers, 250K parameters, and about 27 million
connections.

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 8 layers (5
    convolutional, 3 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

Another issue we observed in training/testing the network, which could
affect the network performance, is camera latency. In DeepPicar's
context, the camera latency is from the time the camera
sensor observes the scene to the time the computer actually reads the
digitized image data. This time can be noticable depending on the camera 
used and the performance of the Pi. We experimentally measured the camera
latency and found it to be around 50-100 ms. This is higher than the 
latency of human perception, which is known to be as fast as 13 
ms~\cite{ThomasBurger2015}. Higher camera latency could negatively 
affect control performance, because the DNN would analyze stale scenes. 
In the future, we plan to identify and use low-latency cameras.
